COG-ED Manuscript

### 2021-10-21 06_Paper/COG-ED/Manuscript.Rmd
tried fixing AUC

@@

  h3_data <- data.frame(subject = character(), auc_sv = double())

@@

    newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
                          auc_sv = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
                                   method = "trapezoid", sort = FALSE))
    h3_data <- rbind(h3_data, newdata)

>>>>

**something is wrong with the AUC calculation**

```{r AUC_demo, echo=FALSE, message=FALSE, warning=FALSE}

require(gtools)
demo_data = data.frame(level = rep(1:4,24))
sv = permutations(n = 4, r = 4, v = c(0.1,0.4,0.85,1))
m = 1
for (n in 1:nrow(demo_data)) {
  demo_data$subject[m:(m+3)] = rep(n,4)
  demo_data$sv[m:(m+3)] = sv[n,]
  m = m + 4
}
subjectindex <- c(1,which(demo_data$subject != dplyr::lag(demo_data$subject)),nrow(demo_data))
demo_sv <- data.frame(subject = character(), auc_sv = double(), auc_sv_unsorted = double())
for (i in 1:(length(subjectindex)-1)) {
  newdata <- data.frame(subject = demo_data$subject[subjectindex[i]],
                          auc_sv = auc(demo_data$level[subjectindex[i]:(subjectindex[i+1]-1)], demo_data$sv[subjectindex[i]:(subjectindex[i+1]-1)],
                                   method = "trapezoid", sort = FALSE),
                          auc_sv_unsorted = (0.5 * (demo_data$sv[subjectindex[i]] + demo_data$sv[subjectindex[i]+1]) +
                                               0.5 * (demo_data$sv[subjectindex[i]+1] + demo_data$sv[subjectindex[i]+2]) +
                                               0.5 * (demo_data$sv[subjectindex[i]+2] + demo_data$sv[subjectindex[i]+3])))
  demo_sv <- rbind(demo_sv, newdata)
}
```

@@

  h3_data <- data.frame(subject = character(), auc_sv = double(), auc_sv_unsorted = double())

@@

    newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
                          auc_sv = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
                                   method = "trapezoid", sort = FALSE),
                          auc_sv_unsorted = (0.5 * (data_SV$sv[subjectindex[i]] + data_SV$sv[subjectindex[i]+1]) +
                                               0.5 * (data_SV$sv[subjectindex[i]+1] + data_SV$sv[subjectindex[i]+2]) +
                                               0.5 * (data_SV$sv[subjectindex[i]+2] + data_SV$sv[subjectindex[i]+3])))
    h3_data <- rbind(h3_data, newdata)
